\let\negmedspace\undefined
\let\negthickspace\undefined
\documentclass[journal]{IEEEtran}
\usepackage[a5paper, margin=10mm, onecolumn]{geometry}
%\usepackage{lmodern} % Ensure lmodern is loaded for pdflatex
\usepackage{tfrupee} % Include tfrupee package

\setlength{\headheight}{1cm} % Set the height of the header box
\setlength{\headsep}{0mm}     % Set the distance between the header box and the top of the text

\usepackage{gvv-book}
\usepackage{gvv}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{txfonts}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{gensymb}
\usepackage{comment}
\usepackage[breaklinks=true]{hyperref}
\usepackage{tkz-euclide} 
\usepackage{listings}
% \usepackage{gvv}                                        
\def\inputGnumericTable{}                                 
                              
\usepackage{color}                                            
\usepackage{array}                                            
\usepackage{longtable}                                       
\usepackage{calc}                                             
\usepackage{multirow}                                         
\usepackage{hhline}                                           
\usepackage{ifthen}                                           
\usepackage{lscape}
\usepackage[utf8]{inputenc}

\usepackage{amsmath}
\begin{document}

\bibliographystyle{IEEEtran}
\vspace{3cm}

\title{2012-CE-53-65}
\author{EE24BTECH11065-spoorthi}
% \maketitle
% \newpage
% \bigskip
{\let\newpage\relax\maketitle}

\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\setlength{\intextsep}{10pt} % Space between text and floats


\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\renewcommand{\thetable}{\theenumi}

\begin{enumerate}
    \item[Q.53] The ultimate moment capacity $\brak{in \ kNm}$ of the section, as per the Limit State Method of IS 456:2000 is 
    \begin{multicols}{4}
    \begin{enumerate}
        \item 200.0
        \item 223.3
        \item 236.3
        \item 273.6
        
    \end{enumerate}
    \end{multicols}
\textbf{Statement for Linked Answer Questions 54 and 55:} \\
 The drainage area of a watershed is 50$km^2$. The $\phi$ index is 0.5 $cm/hour$ and the base flow at the outlet is 10 $m^3/s$. One hour unit hydrograph $\brak{unit depth = 1 cm}$ of the watershed is triangular in shape with a time base of 15 hours. The peak ordinate occurs at 5 hours. 
\item[Q.54] The peak ordinate  $\brak{in \ m^3/s/cm}$ of the unit hydrograph is
\begin{multicols}{4}
\begin{enumerate}
    \item 10.00
    \item 18.52
    \item 37.03
    \item 185.20
\end{enumerate}
    
\end{multicols}
\item[Q.55] For a storm of depth of 5.5$cm$ and duration of 1 hour, the peak ordinate $\brak{in \ m^3/s}$ of the hydrograph is 
\begin{multicols}{4}
\begin{enumerate}
    \item 55.00
    \item 82.60
    \item 92.60
    \item 102.60
\end{enumerate}
    
\end{multicols}
\textbf{General Aptitude \brak{GA} Questions} \\
 \textbf{Q.56 - Q.60 carry one mark each.} \\
 \item[Q.56] Choose the most appropriate alternative from the options given below to complete the following sentence: \\
            
          \textbf{Despite several \underline{\hspace{2cm}} the mission succeeded in its attempt to resolve the conflict.} \\
            \begin{multicols}{4}
            \begin{enumerate}
                \item attempts
                \item setbacks
                \item meetings
                \item delegations
            \end{enumerate}
                
            \end{multicols}
            \item[Q.57] The cost function for a product in a firm is given by $5q^2$ where $q$ is the amount of production. The firm can sell the product at a market price of \rupee  50 per unit. The number of units to be produced by the firm such that the profit is maximized is
\begin{multicols}{4}
    

    \begin{enumerate}
        \item 5
        \item 10
        \item 15
        \item 25
    \end{enumerate} 
    \end{multicols}
\item[Q.58] Choose the most appropriate alternative from the options given below to complete the following sentence:\\

   \textbf{Suresh's dog is the one \underline{\hspace{2cm}} was hurt in the stampede. } 
\begin{multicols}{4}
    

    \begin{enumerate}
        \item that
        \item which
        \item who
        \item whom
    \end{enumerate}
    \end{multicols}

    \item[Q.59] Choose the grammatically \textbf{INCORRECT} sentence:

    

    \begin{enumerate}
        \item They gave us the money back less the service charges of Three Hundred rupees. 
        \item This country's expenditure is not less than that of Bangladesh. 
        \item The committee initially asked for a funding of Fifty Lakh rupees, but later settled for a lesser sum. 
        \item This country's expenditure on educational reforms is very less. 
    \end{enumerate}


    \item[Q.60] Which one of the following options is the closest in meaning to the word given below ?

    \textbf{Mitigate}
    \begin{multicols}{4}
        
    
    \begin{enumerate}
        \item Diminish
        \item Divulge
        \item Dedicate
        \item Denote
    \end{enumerate}
    \end{multicols}



\textbf{Q.61 - Q.65 carry two marks each. } \\

  \item[Q.61] A political party orders an arch for the entrance to the ground in which the annual convention is being held. The profile of the arch follows the equation $y = 2x - 0.1x^2$ where $y$ is the height of the arch in meters. The maximum possible height of the arch is:
\begin{multicols}{4}
    

    \begin{enumerate}
        \item 8 meters
        \item 10 meters
        \item 12 meters
        \item 14 meters
    \end{enumerate}
    \end{multicols}

    \item[Q.62] \textbf{Wanted Temporary, Part-time persons for the post of Field Interviewer to conduct personal interviews to collect and collate economic data. Requirements: High School-pass, must be available for Day, Evening and Saturday work. Transportation paid, expenses reimbursed.} \\

     Which one of the following is the best inference from the above advertisement? 
    

    \begin{enumerate}
        \item Gender-discriminatory
        \item Xenophobic
        \item Not designed to make the post attractive
        \item Not gender-discriminatory
    \end{enumerate}
    

    \item[Q.63] Given the sequence of terms, $AD$ $CG$ $FK$ $JP$, the next term is:
\begin{multicols}{4}
    

    \begin{enumerate}
        \item $OV$
        \item $OW$
        \item $PV$
        \item $PW$
    \end{enumerate}
    \end{multicols}

    \item[Q.64] Which of the following assertions are \textbf{CORRECT}?

    \textbf{P:} Adding 7 to each entry in a list adds 7 to the mean of the list \\
    \textbf{Q:} Adding 7 to each entry in a list adds 7 to the standard deviation of the list \\
    \textbf{R:} Doubling each entry in a list doubles the mean of the list \\
    \textbf{S:} Doubling each entry in a list leaves the standard deviation of the list unchanged
\begin{multicols}{4}
    

    \begin{enumerate}
        \item $P, Q$
        \item $Q, R$
        \item $P, R$
        \item $R, S$
    \end{enumerate}
    \end{multicols}

    \item[Q.65] An automobile plant contracted to buy shock absorbers from two suppliers $X$ and $Y$. $X$ supplies 60\% and $Y$ supplies 40\% of the shock absorbers. All shock absorbers are subjected to a quality test. The ones that pass the quality test are considered reliable. Of $X$'s shock absorbers, 96\% are reliable. Of $Y$'s shock absorbers, 72\% are reliable.\\

     The probability that a randomly chosen shock absorber, which is found to be reliable, is made by $Y$ is:
\begin{multicols}{4}
    

    \begin{enumerate}
        \item 0.288
        \item 0.334
        \item 0.667
        \item 0.720
    \end{enumerate}
    \end{multicols}

     
    
\end{enumerate}




\end{document}



